A Kochen-Specker system has at least 22 vectors

### 2014-12-15 paper/main.tex
paper: Attribute Spitters

We are grateful to prof.~McKay for discussing
the feasibility of certain graph restrictions and
to Judith van Stegeren\footnote{\url{http://jd7h.com/}}
for drawing figures for the draft version of this paper.
\end{acknowledgment}

>>>>

We are grateful to prof.~McKay for discussing the feasibility of
certain graph restrictions; to Bas Spitters for showing us the
article of Arends, Ouaknine and Wampler \emph{and} to Judith van
Stegeren\footnote{\url{http://jd7h.com/}} for drawing figures for
the draft version of this paper.
\end{acknowledgment}
